RDF Validation Requirements - Evaluation and Logical Underpinning

### 2015-06-11 paper/RDF validation requirements/RDF validation requirements.tex
abstract and mapping from constraint types to constraining elements

\begin{itemize}
  \item Constraints of 64\% of all constraint type can be expressed using logical constructs from description logics.
	\item We developed a vocabulary and for each constraint type we identified constraining elements to represent constraints of any constraint type.

	\item In most cases, it is sufficient to use only 1 logical construct
	\item Some combinations of logical constructs can be simplified to 1 logical construct which can be used in terms of syntactic sugar
  \item constraints of the majority of the constraint types can be expressed logically by description logics
	\item constraints of all constraint types can be expressed by constraining elements
	\item For 1 constraint types, there can be multiple constraining elements
	\item the validation of each constraining element has to be implemented
	\item We use SPARQL as extension mechanism to express constraints of 3 constraint types which cannot be expressed otherwise as they are too complex to represent them using a high-level constraint language
\end{itemize}

@@

Optional Properties & $\exists$, $\sqsubseteq$ & optional \\
Repeatable Properties & $\geq$ & repeatable \\
Negative Property Constraints & $\neg$, $\exists$ & negative properties \\
*Individual Equality & = & \\
*Functional Properties & functional & \\ 
*Inverse-Functional Properties & inverse, functional & inverse functional \\
*Value Restrictions & $\exists$ & value restriction \\
*Self Restrictions & $\exists$ & self restriction \\
Primary Key Properties & inverse, functional & keyfor or primary key \\
*Class-Specific Property Range & $\sqsubseteq$, $\exists$, $\neg$ & range \\
*Class-Sp. Reflexive Object P. & reflexive & \\
Membership in Controlled Vocabularies & $\forall$, $\sqcap$, $\sqcup$ & membership in \\
  && controlled vocabularies \\
IRI Pattern Matching & - & IRI pattern matching \\
Literal Value Comparison & $>$ or $\geq$ or $<$ or & \\
                         & $\leq$ or = or $\ne$ & \\
Ordering & - & order \\ 
Validation Levels & - & validation level \\ 
String Operations & - & SPARQL string operations \\ 
  && examples: STRLEN, \\ 
	&& SUBSTR, CONTAINS \\
Context-Specific Valid Classes & - & context-specific valid classes \\
Context-Specific Valid Properties & - & context-specific valid properties \\
Default Values & - & default values \\
Mathematical Operations & - & example: multiplication \\
Language Tag Matching & - & language tag matching \\
Language Tag Cardinality & - & language tag minimum cardinality, \\
                            && language tag maximum cardinality, \\
													  && language tag exact cardinality \\
Whitespace Handling & - & whitespace \\
HTML Handling & - & html \\
Conditional Properties & $\sqsubseteq$ & conditional \\
Recommended Properties & - & recommended \\
Handle RDF Collections & - & actions on RDF collections \\
Value is Valid for Datatype & - & value is valid for datatype \\
Use Sub-Super Relations in Validation & - & not redundant \\
*Cardinality Shortcuts & & optional \& non-repeatable, \\
                       & & optional \& repeatable \\
											 & & mandatory \& non-repeatable \\
											 & & mandatory \& repeatable \\
Aggregations & - & aggregations \\
                 && e.g., count \\
*Class-Specific Irreflexive Object Properties & reflexive, $\neg$ & irreflexive \\
Provenance & - & provenance \\   
Data Model Consistency & - & SPARQL \\    
Structure & - & SPARQL \\  
Labeling and Documentation & - & SPARQL \\   
Vocabulary & - & vocabulary \\  
HTTP URI Scheme Violation & - & HTTP URI scheme violation \\

>>>>

\begin{itemize}
  \item Constraints of 64\% of all constraint type can be expressed using logical constructs from description logics.	
	\item For a constraint types, there can be multiple constraining elements
	\item The validation of each constraining element has to be implemented
	\item We use SPARQL as extension mechanism to express constraints of 3 constraint types which cannot be expressed otherwise as they are too complex to represent them using a high-level constraint language
\end{itemize}

@@

Optional Properties & $\exists$, $\sqsubseteq$ & optional properties \\
Repeatable Properties & $\geq$ & repeatable properties \\
Negative Property Constraints & $\neg$, $\exists$ & negative properties \\
*Individual Equality & = & \\
*Functional Properties & functional & \\ 
*Inverse-Functional Properties & inverse, functional & inverse functional \\
*Value Restrictions & $\exists$ & value restriction \\
*Self Restrictions & $\exists$ & self restriction \\
Primary Key Properties & inverse, functional & keyfor or primary key \\
*Class-Specific Property Range & $\sqsubseteq$, $\exists$, $\neg$ & range \\
*Class-Sp. Reflexive Object P. & reflexive & \\
Membership in Controlled Vocabularies & $\forall$, $\sqcap$, $\sqcup$ & membership in \\
  && controlled vocabularies \\
IRI Pattern Matching & - & IRI pattern matching \\
Literal Value Comparison & $>$ or $\geq$ or $<$ or & \\
                         & $\leq$ or = or $\ne$ & \\
Ordering & - & order \\ 
Validation Levels & - & validation level \\ 
String Operations & - & SPARQL string operations \\ 
  && examples: STRLEN, \\ 
	&& SUBSTR, CONTAINS \\
Context-Specific Valid Classes & - & context-specific valid classes \\
Context-Specific Valid Properties & - & context-specific valid properties \\
Default Values & - & default values \\
Mathematical Operations & - & example: multiplication \\
Language Tag Matching & - & language tag matching \\
Language Tag Cardinality & - & language tag minimum cardinality, \\
                            && language tag maximum cardinality, \\
													  && language tag exact cardinality \\
Whitespace Handling & - & whitespace \\
HTML Handling & - & html \\
Conditional Properties & $\sqsubseteq$ & conditional \\
Recommended Properties & - & recommended \\
Handle RDF Collections & - & actions on RDF collections \\
Value is Valid for Datatype & - & value is valid for datatype \\
Use Sub-Super Relations in Validation & - & not redundant \\
*Cardinality Shortcuts & & optional \& non-repeatable, \\
                       & & optional \& repeatable \\
											 & & mandatory \& non-repeatable \\
											 & & mandatory \& repeatable \\
Aggregations & - & aggregations \\
                 && e.g., count \\
*Class-Specific Irreflexive Object Properties & reflexive, $\neg$ & irreflexive \\
Provenance & - & provenance \\   
Data Model Consistency & - & SPARQL \\    
Structure & - & SPARQL \\  
Labeling and Documentation & - & SPARQL \\   
Vocabulary & - & vocabulary \\  
HTTP URI Scheme Violation & - & HTTP URI scheme violation \\
